How Well do we Teach Cybersecurity?

### 2018-11-24 ITiCSE2019.tex
JHD had a start

\begin{document}
\title{What Do We Mean By Cybersecurity?}
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\section{introduction}

And here we go...

>>>>

\begin{document}
\title{How Well do we Teach Cybersecurity?}
%\title{What Do We Mean By Cybersecurity?}  Tom's original was this
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\section{Introduction}

Cybersecurity has been in the news for several years, generally prompted by spectacular breaches of one kind or another, such as \cite{BritishAirways2018a}.

There are calls for education to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}.

Nevertheless, it is one thing to write curricula and requirements, and another thing to deliver appropriate education, and one could reasonably ask how well this is done in practice.

\section{Challenges}

\subsection{Educational Resources}
JHD to write about Database books.

\subsection{Staff}
JHD possibly to write about his recruitment experiences.  ? more IoC input?

\subsection{Accreditation}
?AI/TP to write something.
